---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
<!-- badges: end -->

The goal of bis620.2022 is to 

1. Capture spectral signature of Accelerometry data with three dimensions using Fast Fourier Transform (FFT) and also calculate frequency with time.

2. Create a visualization for movements in three dimensions with time or frequency.

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bis620.2022")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bis620.2022)
## basic example code
#to get FFT of dimensions and frequency from time
data("ukb_accel")
ukb_accel |> spectral_signature()
#to create visualization of movement with time
ukb_accel |> accel_plot()
#to create visualization of logarithm transformed FFT
#movement with frequency
ukb_accel |> spectral_signature(take_log = T) |> accel_plot()
```
